Supporting online material for\\ \emph{Effectiveness of UNAIDS targets and HIV vaccination across 127 countries}

### 2016-08-20 Documents/supplementary_text.tex
Removed section on log variables.

\section{Numerical solution}

For accuracy and speed in numerically solving differential equations
\eqref{model_eqns}, the variables $S$, $U$, $D$, $T$, $V$, and
$W$---i.e., those that are not initially $0$---were log transformed
and the differential equations were written in terms of
the new log variables:
\begin{equation}
  \label{model_eqns_log}
  \begin{split}
    \frac{\md \log S}{\md t} &= \kappa N \me^{- \log S} - \lambda - \zeta - \mu,
    \\
    \frac{\md R}{\md t} & = \zeta \me^{\log S} - (1 - \rho) \lambda R - \mu R,
    \\
    \frac{\md A}{\md t} &= \lambda \me^{\log S} + (1 - \rho) \lambda R
    - \delta A - \mu A,
    \\
    \frac{\md \log U}{\md t} &= \delta A \me^{- \log U} - \alpha - \mu - \sigma,
    \\
    \frac{\md \log D}{\md t} &=  \alpha \me^{\log U - \log D}
    + \psi \me^{\log T - \log D} + \psi \me^{\log V - \log D} - \phi - \mu - \sigma,
    \\
    \frac{\md \log T}{\md t} &= \phi \me^{\log D - \log T} - \psi - \gamma - \mu
    - \sigma,
    \\
    \frac{\md \log V}{\md t} &= \gamma \me^{\log T - \log V} - \psi
    - \mu  - \theta,
    \\
    \frac{\md \log W}{\md t} &= \sigma \me^{\log U - \log W}
    + \sigma \me^{\log D - \log W} + \sigma \me^{\log T - \log W}
    + \theta \me^{\log V - \log W} - \nu,
    \\
    \frac{\md Y}{\md t} &= \lambda \left[\me^{\log S} + (1 - \rho) R\right],
    \\
    \frac{\md Z}{\md t} &= \nu \me^{\log W}.
  \end{split}
\end{equation}

The model simulation and analysis tools, written in Python, are
publicly available at
\url{https://github.com/janmedlock/HIV-95-vaccine/}
\cite{medlock2016-git}.  The differential equations were solved using
\texttt{scipy.integrate.odeint()} \cite{scipy}.  See the source code
for full details.

@@

>>>>

@@

\section{Source code}

The model simulation and analysis tools, written in Python, are
publicly available at
\url{https://github.com/janmedlock/HIV-95-vaccine/}
\cite{medlock2016-git}.
